%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bf
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}] %
%\titleformat{\section}{
%  \vspace{-4pt}\scshape\raggedright\large
%}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadingone}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    %\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {#2}
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheadingtwo}[2]{
    \item\vspace{-2pt}
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & {\small #2}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingthree}[2]{
    \item\vspace{-2pt}
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {\small#1} & {\small #2}
    \end{tabular*}\vspace{-7pt}
}

%\newcommand{\resumeSubheading}[4]{
%  \vspace{-2pt}\item
%    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%      \textbf{#1} & #2 \\
%      \textit{\small#3} & \textit{\small #4} \\
%    \end{tabular*}\vspace{-7pt}
%}

\newcommand{\resumeSubSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

%\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny}}$}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
%\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
%\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Large \scshape Hyeonjae Cho} \\ \vspace{2pt}
    \small Email:  \href{mailto:ilovelatale@yonsei.ac.kr}{{ilovelatale@yonsei.ac.kr}} $|$ 
    \href{https://blog.naver.com/ilovelatale}{{blog.naver.com/ilovelatale}}
    $|$ 
    \href{https://github.com/myevertime}{{github.com/myevertime}}
    %\small Phone: +82-10-2703-1052 $|$ \href{mailto:x@xcom}{\underline{x.x.com}} $|$ 
    %\href{https://linkedin.com/in/x}{\underline{linkedin.com/in/x}} $|$
    %\href{https://github.com/x}{\underline{github.com/x}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingone
      {Yonsei University}{Seoul, Korea}
    \resumeSubheadingtwo
      {Undergraduate Student}{Mar. 2016 – Feb. 2020}
          \resumeItemListStart
            \resumeItem{Bachelor of Arts in Economics}
            \resumeItem{Bachelor of Science in Computer Science and Engineering}
            \resumeItem{Total GPA of 4.1/4.3 (97/100); Graduated with High Honors}
        \resumeItemListEnd
  
    \resumeSubheadingone
      {George Washington University}{Washington D.C., U.S.}
    \resumeSubheadingtwo
      {Exchange Student}{Jan. 2018 – May 2018}
          \resumeItemListStart
            \resumeItem{Total GPA of 3.74/4.0}
        \resumeItemListEnd

    \resumeSubheadingone
      {University of Illinois Urbana-Champaign}{Urbana-Champaign, IL, U.S.}
    \resumeSubheadingtwo
      {Graduate Student}{May. 2022 – August 2023}
          \resumeItemListStart
            \resumeItem{Master of Computer Science}
            \resumeItem{Total GPA of 4.0/4.0}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Undergraduate Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheadingone
      {Yonsei University Super Computing Lab}{Seoul, Korea}
    \resumeSubheadingtwo
      {Undergraduate Researcher}{Sep. 2019 – Dec. 2019}
      \resumeItemListStart
        \resumeItem{Implemented cache replacement policy using K-means algorithm to enhance last level cache hit rate with less overhead}
        \resumeItem{Authored semifinal and final reports and created exhibition presentation materials}$|$\href{https://drive.google.com/file/d/1tdWqPrcHN92vLKJEBgHGemGQFwEZ92RH/view?usp=sharing}{{pdf}}$|$

      \resumeItemListEnd
      
    \resumeSubheadingone
      {Yonsei University Internet Computing Lab}{Seoul, Korea}
    \resumeSubheadingtwo
      {Undergraduate Researcher}{Mar. 2019 – May 2019}
      \resumeItemListStart
        \resumeItem{Analyzed the weaknesses of the knowledge graph-based model, RippleNet, by applying it to open data sources}
        \resumeItem{Visualized network graphs of RippleNet to focus on extreme data and to extract logical and implemental errors}$|$\href{https://drive.google.com/file/d/1GwyKr07edwbqXFtQKAicSukckHUZCxce/view?usp=sharing}{{pdf}}$|$
      \resumeItemListEnd

    \resumeSubheadingone
      {Ministry of Science and ICT}{Seoul, Korea}
    \resumeSubheadingtwo
      {Team Leader, Industry Research Team}{Apr. 2019 – Dec. 2019}
      \resumeItemListStart
        \resumeItem{Government-funded project; Budget: \$68,000}
        \resumeItem{Categorized the key players of various industries by examining the blockchain ecosystem}
        \resumeItem{Assessed the progress of technological advancements of each industry}
        \resumeItem{Contributed toward establishing a strategy to enhance the blockchain industry in Korea}$|$\href{https://drive.google.com/file/d/1kpkAC4pYRuef8tJ8R6AqpmA0R4nICGkl/view?usp=sharing}{{pdf}}$|$
      \resumeItemListEnd      
     
    \resumeSubHeadingListEnd

%-----------Work Experience-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheadingone
      {SK Telecom Co., Ltd.}{Seoul, Korea}
    \resumeSubheadingtwo
      {Data Analyst, Ad Tech Team}{Jan. 2020 – Present}
      \resumeItemListStart
        \resumeItem{Operate targeted advertising campaigns with machine learning models and improve their performances}
        \resumeItem{Improve sales by 20\% by developing a recommendation system using service transaction logs}
        \resumeItem{Spearhead data engineering tasks with AWS resources and Spark to aggregate major business performance indicators}
        \resumeItem{Selected as an {\it additional contributor} for achievements within the organization}
      \resumeItemListEnd
      
    \resumeSubheadingtwo
      {Intern, Metatron Sales Team}{Jun. 2019 – Aug. 2019}
      \resumeItemListStart
        \resumeItem{Investigated strengths and weaknesses of representative business intelligence (BI) tools and analyzed market trends to recommend a suitable positioning strategy for an in-house BI solution}
      \resumeItemListEnd

    \resumeSubheadingone
      {Ground X Corp.}{Seoul, Korea}
    \resumeSubheadingtwo
      {Research Assistant, Token Economy Team}{Jan. 2019 – Feb. 2019}
      \resumeItemListStart
        \resumeItem{Classified and analyzed Ethereum token standards by inspecting Ethereum token economy ecosystems}
        \resumeItem{Collected blockchain transaction data by establishing full nodes for EOS and TRON utilizing AWS EC2 resources}
      \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------Awards and Honors-----------
\section{Awards and Honors}
  \resumeSubHeadingListStart

    \resumeSubheadingthree
      {{\bf 2nd Prize in Yonsei Big Data Analysis Competition}, Yonsei University}{Sep. 2018}
    \resumeSubheadingthree
      {Academic Excellence Scholarship, Yonsei University}{Spring 2019, Fall 2017, Fall 2016}
    \resumeSubheadingthree
      {Yonsei Honors}{Spring 2019, Fall 2018}
    \resumeSubheadingthree
      {Yonsei Highest Honors}{Spring 2017, Spring 2016}
      
    \resumeSubHeadingListEnd

%-----------Leadership Experience-----------
\section{Leadership Experience}
  \resumeSubHeadingListStart

    \resumeSubheadingone
      {Yonsei University Blockchain Club}{Seoul, Korea}
    \resumeSubheadingtwo
      {Vice President}{Jan. 2019 – Jun. 2019}
      \resumeItemListStart
        \resumeItem{Executed an industry research team for a government-funded project at the Ministry of Science and ICT}
        \resumeItem{Voluntarily orchestrated seminars on the token economy ecosystem and token standards}
      \resumeItemListEnd

    \resumeSubheadingone
      {Yonsei University Big Data Analysis Competition}{Seoul, Korea}
    \resumeSubheadingtwo
      {Team Leader}{Sep. 2018}
      \resumeItemListStart
        \resumeItem{Tokenized social media reviews data to determine brand awareness and images}
        \resumeItem{Conducted sentiment and association analyses to suggest a marketing strategy} $|$\href{https://github.com/myevertime/2018-Big-data-Contest}{{code}}$|$
      \resumeItemListEnd

    \resumeSubHeadingListEnd
    
%-----------PATENTS AND PATENT APPLICATIONS-----------
\section{Patent Applications}
  \resumeSubHeadingListStart

    \resumeSubheadingthree
      {Korea Patent Application 10-2021-0108767}{Oct. 18, 2021}
     \resumeSubheadingtwo
      {A method for triggering mode decision and a message-based advertising platform}{}
      \resumeItemListStart
        \resumeItem{Patent for an algorithm that predicts customer preferences based on machine learning and assigns specific advertising campaigns to be sent via text message}
      \resumeItemListEnd
      
    \resumeSubHeadingListEnd

%-----------Extra Curricular Activities-----------
\section{Extracurricular Activities}

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Personal Tech Blog}}{\small Jan. 2021 – Present}
          \resumeItemListStart
            \resumeItem{Study MLOps, AWS, Growth Hacking, ML/DL algorithms} $|$\href{https://blog.naver.com/ilovelatale}{{blog}}$|$
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Bandit for Recommendation System}} {\small May 2021 – Jul. 2021}
          \resumeItemListStart
            \resumeItem{Examined papers and codes of Multi-Armed Bandit (MAB) recommendation system, such as contextual bandit, stochastic bandit, and collaborative filtering bandit}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Scala, SQL, Java, C++, Bash} \\
     \textbf{Cloud Technologies}{: AWS(Glue, S3, EC2, ECS, CloudWatch), GCP(BigQuery)} \\
     \textbf{Frameworks}{: TensorFlow, PyTorch, Keras, scikit-learn} \\
     \textbf{Databases}{: MySQL, Amazon Athena, Apache Spark, PostgreSQL} \\
     \textbf{Tools}{: Docker, GitHub, Google Analytics, Google Tag Manager, Google Optimize} \\
     
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
